Measuring Perceptions and Preferences for Meritocracy

### 2021-01-15 docs/paper.Rmd
Traduccion
Se analiza la validez convergente en orden segun las escalas utilizadas para el contraste.

Se traduce al ingles y mejora la redacción.

For this analysis we examined information of the third wave of the study, which included additional measures that allow testing the correlations of the merit scale with some related constructs as opportunity beliefs and personal wherewithal. After listwise deletion of missing cases in socio-demographics information, a total of 1422 individuals took part in the third wave: 668 (46.97%) women and 754 (53.03%) men. The ages of 50.57% of them are 45 years or older, and 36.28% held a tertiary degree.1

@@

The following scales were included for testing their correlation with the the 8-item meritocracy scale:

- Opportunity beliefs: We used two items of the social inequality module of the International Social Survey Programme. Studies use generally both indicators to measure meritocratic and non-meritocratic beliefs [@McCall2017Exposurerisinginequality; @mijs_paradox_2019].  One item measures the importance of individual factors in determining life outcomes by asking for the importance of hard work for getting ahead in life (M=3.76, SD=0.93). The second item asks for the importance of coming from a wealthy family and captures the importance of structural factors in getting ahead (M=2.75, SD=1.27). Participants responded to each item using a 1 (not at all important) to 5 (essential) response scale.

- Personal wherewithal: the questionnaire included The Neoliberal Beliefs Inventory (NBI), which consider four factors: Government Interference preferences, Competition preferences, System Inequality perception and Personal Wherewithal [@bay-chengTrackingHomoOeconomicus2015]. We used the factor personal wherewithal that reflects meritocracy beliefs in terms of the importance of personal attributes as strength and skills to yield success. The construct consists of 8 items (e.g., “Any goal can be achieved with enough hard work and talent”, “I’ve benefited from working hard, so there’s no reason others can’t”, “Anyone who is willing to work hard can be succesful in Chile”). Participants answered the items using a 1 (totally disagree) to 6 (totally agree) scale. We simple computed mean scores [reportar alfa the cronbach], with higher scores indicating stronger support for meritocracy (M=3.32, SD=0.88, $\alpha$ = 0.89).

@@

Table \@ref(tab:val-conv) table shows the polyserial and pearson correlations between the PPM-S and other common measures of meritocracy. The findings provide evidence for convergent validity for the scale. En términos generales como era esperable las preferencias poseen relaciones de menor intensidad con estas escalas que son utilizadas usualmente para medir percepciones. A continuación, evaluamos la relación de ambas escalas con las dimensiones de PPM-S

|                                      |     Origen     |     Hard Work    |     Wherewithal    |
|--------------------------------------|----------------|------------------|--------------------|
|     Meritocratic     Perception      |     -0,1975    |     0,1877       |     0,3921         |
|     Unmeritocratic    Perception     |     0,3547     |     -0,0775      |     -0,1844        |
|     Meritocratic    Preferences      |     0,1078     |     0,0779       |     0,0819         |
|     Unmeritocratic    Preferences    |     -0,0397    |     0,0824       |     0,2082         |
Table: `r as.character(paste("(\\#tab:val-conv)", "Polyserial and Pearson correlation whit other merit scales"))`.

Los dos indicadores de la batería “salir a delante” se correlacionan coherentemente, pero con una intensidad de moderada a baja. Considerar importante tener padres con recursos para salir a delante posee una asociación positiva de moderada intensidad con la percepción de distribución no meritocrática (r = .354) y una relación negativa de baja intensidad con percepción meritocrática (-0.197), lo cual constituye una evidencia de valides considerando la relación entre los constructos. Por su parte, la importancia asignada trabajar duro para salir adelante solo se relaciona débilmente con la percepción de meritocrática (r = .187).

La dimensión de la escala NBI “Creer que los recursos personales producen el éxito” posee una relación positiva de moderada intensidad con la percepción de meritocracia (r = .392), lo cual constituye una evidencia de valides considerando que miden conceptos parcialmente similares. La escala de recursos personales también se asocia débil pero positivamente a las preferencias no meritocraticas (r = .208). Esta asociación es coherente tomando en cuenta que la creencia en la meritocracia se asocia a la justificación de distintas desigualdades [@mccoy_Priming_2007;@MadeiraPrimesConsequencesSystematic2019] y considerando que dentro de nuestra escala PPM-S la percepción de meritocracia y la preferencia no meritocracia también se relacionan positiva y débilmente.

>>>>

For this analysis we examined information of the third wave of the study, which included additional measures that allow testing the correlations of the merit scale with some related constructs as opportunity beliefs and personal wherewithal. After listwise deletion of missing cases in socio-demographics information, a total of 1422 individuals took part in the third wave: 668 (46.97%) women and 754 (53.03%) men. The ages of 50.57% of them are 45 years or older, and 36.28% held a tertiary degree.

@@

The following scales were included for testing their correlations with the the 8-item meritocracy scale:

  - Opportunity beliefs: We used two items of the social inequality module of the International Social Survey Programme. Studies use generally both indicators to measure meritocratic and non-meritocratic beliefs [@McCall2017Exposurerisinginequality; @mijs_paradox_2019].  One item measures the importance of individual factors in determining life outcomes by asking for the importance of hard work for getting ahead in life (M=3.76, SD=0.93). The second item asks for the importance of coming from a wealthy family and captures the importance of structural factors in getting ahead (M=2.75, SD=1.27). Participants responded to each item using a 1 (not important at all) to 5 (essential) response scale. We call the first item \textit{hard work} and the second one \textit{social origin}.

- Personal wherewithal: the questionnaire included The Neoliberal Beliefs Inventory (NBI), which consider four factors: Government Interference preferences, Competition preferences, System Inequality perception and Personal Wherewithal [@bay-chengTrackingHomoOeconomicus2015]. We used the factor personal wherewithal that reflects meritocracy beliefs in terms of the importance of personal attributes as strength and skills to yield success. The construct consists of 8 items (e.g., “Any goal can be achieved with enough hard work and talent”, “I’ve benefited from working hard, so there’s no reason others can’t”, “Anyone who is willing to work hard can be succesful in Chile”). Participants answered the items using a 1 (totally disagree) to 6 (totally agree) scale. We simple computed mean scores, with higher scores indicating stronger support for meritocracy (M=3.32, SD=0.88, $\alpha$ = 0.89).

@@

Table \@ref(tab:val-conv) table shows the polyserial and pearson correlations between the PPM-S and common measures of meritocracy. The findings provide evidence for convergent validity for the scale. As we expected, preferences show very weak correlations. Findings also indicate that correlations of perceptions with opportunity beliefs are consistent with our expectations. The item for social origin shows a positive and moderate association with meritocratic perception (r=.354), and a negative and low correlation with meritocratic perception (-0.197). Regarding the item of hard work, the correlation with meritocratic perception is positive but weak (r=.187). One explanation for this result is that the support for hard work is very high among respondents---only 8.6 percent indicate \textit{not very important} or \textit{noy importat at all}.

  |                                      | Social Origin  |     Hard Work    |     Wherewithal    |
  |--------------------------------------|----------------|------------------|--------------------|
  |     Meritocratic     Perception      |     -0.1975    |     0.1877       |     0.3921         |
  |     Unmeritocratic    Perception     |     0.3547     |     -0.0775      |     -0.1844        |
  |     Meritocratic    Preference       |     0.1078     |     0.0779       |     0.0819         |
  |     Unmeritocratic    Preference     |     -0.0397    |     0.0824       |     0.2082         |
  Table: `r as.character(paste("(\\#tab:val-conv)", "Polyserial and Pearson correlation whit other merit scales"))`.

Findings the measure of NBI for \textit{personal wherewithal} also provide evidence for the convergent validity of PPM-S. Results indicate a positive correlation of this measure with meritocratic preference (r=.392), suggesting that both variables capture similar concepts. The NBI's factor depicts a positive association with unmeritocratic preference (r=.208). This finding is consistent with literature, inasmuch as the belief for meritocray is associated with the justification of inequality [@mccoy_Priming_2007;@MadeiraPrimesConsequencesSystematic2019]. Furthermore, results of our confirmatory factor analysis indicate that meritocratic perception and unmeritocratic preferences shows a positive and weak correlation.
